### 2016-05-09 sec4_system.tex
Further edits on Sec1 and sec4

\section{Overview of Mining GCMP in Parallel}
\label{sec:system_overview}
We adapt the MapReduce paradigm for designing
a parallel solution of mining GCMP. In this section,
we briefly cover the preliminary on MapReduce and then describe
the overview of our framework in mining GCMP.

\subsection{Preliminary on MapReduce}
MapReduce (MR) was formally proposed by Dean et. al.~\cite{dean2008mapreduce}
and has subsequently implemented by many open source systems. Those systems
provide handy APIs with fualt tolerances and are popularly
used as large-scale data processing platforms. 
% become a ubiquitous parallel platform for large-scaled data processing. 
%Current open source MapReduce systems provide handy programming APIs with fault tolerances
%in backends. Such systems include Hadoop, Shark and Spark to name a few.
In simple words, there are two conceptual types of computing nodes in MR,
namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
algorithm consists of three stages: First, input data
are partitioned and read by a \emph{map} function on each mapper. Then, mappers
emit key-value pairs which are \emph{shuffle}d over the network to reducers. Finally,
reducers process received data using a \emph{reduce} function then write the
outputs.

Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
First, since it requires reducers to be independent, partitioning  
data to fit the independence could be challenging. Second, since the \emph{shuffle}
stage requires network access, the data been shuffled should be minimized. 
We take these concerns in consideration in designing our solutions for mining GCMP.
%We would bare this concerns in designing our GCMP mining algorithm.
%a natural
%problem is how to partition the data in map and shuffle phase so that reducers 
%achieve the independence.
%
%A critical question in designing a MapReduce algorithm is how to make 
%data partitions during the shuffle stage. In fact, a MapReduce algorithm 
%requires data processed at each reducer to be independent.
%
%Since the \emph{shuffle} stage needs to transfer data over network, 
%an important attention to pay during designing MapReduce an algorithm is 
%to minimize the shuffle amounts and shuffle counts.

\subsection{MapReduce Processing for Mining GCMP}
Our GCMP mining process consists of two MR jobs. The two jobs
contains four MR stages as illustrated in Figure~\ref{fig:overview}.
The first MR job is to cluster objects at each snapshot (i.e.,
computing $\forall t, o, C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
trajectories are first reorganized by timestamps in map phase and object locations
at the same timestamps form a cluster. The clustering takes place in reduce phase, where
each snapshot is processed independently. The second MR job is to mine GCMPs from 
clusters at each snapshot. We design two MR algorithms (i.e., TRM and SPM) for 
the purpose of comparison. Both the two algorithms would partition snapshots in map phase
(as in Figure~\ref{fig:overview}(c))
and mine GCMPs from each partition in reduce phase(as in Figure~\ref{fig:overview}(d)).

@@

Although we need two MR jobs to complete the GCMP mining task, 
it is easy to pipeline the two jobs to exploit data locality.
Specifically, the reducer output at step (b) can be directly reused 
as the input to mappers at step (c). Therefore we do not need to 
transfer data from (b) to (c). Modern MR platforms, especially Spark, have
already supported such a kind of pipeline.

@@

We note that the first MR job is easy to design since each reducer only
needs one snapshot for clustering.
In contrast, it is challenging to design the second job. 
This is because valid patterns may spray across multiple snapshots, where inappropriate partitioning
of snapshots may fail to discover certain valid patterns.
Formally, a reasonable partition strategy 
needs to meet the following requirements: (a) the resulted partitions need
to preserve enough information so that real patterns can be discovered in the reduce phase. 
(b) the resulted partitions need to ensure that
the patterns discovered in the reduce phase are valid patterns so that
no further verification is required. We formalize the two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ such that $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
\end{definition}
The completeness ensures that no true patterns are missed out. 
The soundness ensures that no false patterns are reported. 
If a partition method is both sound and complete, then it can be used
in the second MR job to facilitate GCMP mining.

>>>>

\section{Overview of Mining GCMP in Parallel}
\label{sec:system_overview}
We adapt the MapReduce paradigm for designing
a parallel solution of mining GCMP. In this section,
we briefly describe the preliminaries on MapReduce and then describe
the overview of our framework in mining GCMP.

\subsection{Preliminary on MapReduce}
MapReduce (MR) was formally proposed by Dean et. al.~\cite{dean2008mapreduce}
and has subsequently implemented by many open source systems. Those systems
provide handy APIs with fualt tolerances and are popularly
used as large-scale data processing platforms. 
% become a ubiquitous parallel platform for large-scaled data processing. 
%Current open source MapReduce systems provide handy programming APIs with fault tolerances
%in backends. Such systems include Hadoop, Shark and Spark to name a few.
In simple words, there are two conceptual types of computing nodes in MR,
namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
algorithm consists of two stages: First, input data
are partitioned and read by a \emph{map} function on each mapper. Mappers
emit key-value pairs which are \emph{shuffle}d over the network to reducers. Second,
reducers process the received data using a \emph{reduce} function then write the
outputs.

Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
First, since reducers are required to be independent, partitioning  
data to fit the independence could be challenging. Second, since the \emph{shuffle}
stage requires network access, the data been shuffled should be minimized. 
We take these concerns in consideration when designing our solutions for mining GCMP.
%We would bare this concerns in designing our GCMP mining algorithm.
%a natural
%problem is how to partition the data in map and shuffle phase so that reducers 
%achieve the independence.
%
%A critical question in designing a MapReduce algorithm is how to make 
%data partitions during the shuffle stage. In fact, a MapReduce algorithm 
%requires data processed at each reducer to be independent.
%
%Since the \emph{shuffle} stage needs to transfer data over network, 
%an important attention to pay during designing MapReduce an algorithm is 
%to minimize the shuffle amounts and shuffle counts.

\subsection{MapReduce Processing for Mining GCMP}
Our GCMP mining process consists of two MR jobs, which are further
divided into four MR stages as illustrated in Figure~\ref{fig:overview}.
The first MR job is to cluster objects at each snapshot (i.e.,
 $\forall t, o,$ compute $C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
in map phase, trajectories are first reorganized by timestamps and object locations
at the same timestamps form a cluster. In reduce phase, clustering of objects at each
snapshot is processed independently. The second MR job is to mine GCMPs from 
clusters in each snapshot. We design two MR algorithms (i.e., TRM and SPM) for 
the purpose of comparison. Both the two algorithms would partition snapshots in map phase
(as in Figure~\ref{fig:overview}(c))
and mine GCMPs from each partition in reduce phase(as in Figure~\ref{fig:overview}(d)).

@@

Although we need two MR jobs to complete the GCMP mining task, 
it is easy to pipeline the two jobs to exploit data locality.
Specifically, the reducer output at step (b) can be directly reused 
as the input to the mappers at step (c). Therefore we do not need to 
transfer data between the two jobs. Modern MR platforms, especially Spark, have
already supported such a kind of pipeline by default.

@@

We note that the first MR job is easy to design since each reducer only
needs one snapshot for clustering.
In contrast, it is challenging to design the second job. 
This is because valid patterns may spray across multiple snapshots or contain different object sets, where inappropriate partitioning
of snapshots may fail to discover certain valid patterns.
Formally, a valid partition strategy 
needs to meet the following requirements: (a) the resulted partitions need
to preserve enough information so that real patterns can be discovered in the reduce phase. 
(b) the resulted partitions need to ensure that
the patterns discovered in the reduce phase are valid patterns so that
no further verification is required. We formalize these two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ s.t. $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns that are valid in any $Par_i$, they are also valid in $TR$.
\end{definition}
The completeness ensures that no true patterns are missed out. 
The soundness ensures that no false patterns are reported. 
If a partition method is both sound and complete, then it can be used
in the second MR job to facilitate GCMP mining.

### 2016-05-09 sec5_baseline.tex
Further edits on Sec1 and sec4

\section{Temporal Replication and Mining}
\label{sec:trm_solution}
The \emph{temporal-based} method of mining GCMP follows the solution framework 
as in Figure~\ref{fig:overview}. The idea of the \emph{temporal-based} method 
is to group temporally closed snapshots together, such that patterns can be
mined on each group of the snapshot.
In order to achieve the \emph{completeness}
and \emph{soundness} during partitioning, we design a \emph{Temporal Replication
and Mining} (TRM) algorithm as shown in Algorithm~\ref{algo:trm_overview}.

@@

As shown in Algorithm~\ref{algo:trm_overview}, the \emph{Temporal Replication and Mining} (TRM) algorithm takes
three steps. First, in map phase, each snapshots is keyed with is timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). Second, in the partition phase, every snapshot is grouped with its next $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). We will shortly discuss how the group size is determined. Third, in the reduce phase, a lineSweepMining method is invoked to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ times.

>>>>

\section{Temporal Replication and Mining}
\label{sec:trm_solution}
The idea of \emph{Temporal Replication and Mining} (TRM)
is to group temporally closed snapshots together, such that patterns can be
mined on each group of the snapshot. In order to achieve the \emph{completeness}
and \emph{soundness} during partitioning, we allow replication of
snapshots among groups. The TRM is described in Algorithm~\ref{algo:trm_overview}.

@@

As shown in Algorithm~\ref{algo:trm_overview}, the TRM algorithm takes
three steps. First, in the map phase, each snapshot is keyed with its timestamp (lines~\ref{code:trm-map-start}-\ref{code:trm-map-end}). Second, in the partition phase, every snapshot is grouped with its next $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ snapshots to form a partition (lines~\ref{code:trm-par-start}-\ref{code:trm-par-end}). We will shortly discuss how the group size is determined. Third, in the reduce phase, a lineSweepMining method is invoked to mine GCMP within each partition (lines~\ref{code:trm-red-start}-\ref{code:trm-red-end}). 
It is easy to see that this method replicates a snapshots at most $(\lfloor \frac{K}{L} \rfloor -1)*G+K+L$ times.
